Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex

\begin{abstract}
This paper addresses the issue of creating modular, extensible code given an
existing solution to a problem, namely, interactively modeling large street
networks. We describe a functional implementation of a framework that allows
users to create a realistic street network over an empty domain, based on the
techniques described
in [Chen]. In particular, we were able to express the underlying mathematics
more intuitively and clearly than is possible in an imperative language.

\end{abstract}

\section{Introduction}
Visual artists often face the time-consuming task of generating extensive,
realistic scenes by hand for movies and video games. However, the apparent
randomness found in systems like street layouts can be modelled effectively
with a variety of mathematical algorithms, giving rise to the growing field of
procedural generation. In this paper we will discuss an algorithm using tensor
fields, from [Chen], to generate realistic city street maps. To facilitate the
generation of aesthetically pleasing maps which fit an artist's requirements,
we implement a simple system of user-specified constraints to allow the user to
shape the resulting street map to fit their needs.

@@

\section{Mathematical Background}
\label{sec:math}
A tensor $t$ is a *magical thing* represented by a 2x2 symmetric, traceless
matrix:
\[
    \sqmat{\cos{2\theta}}{\sin{2\theta}}{\sin{2\theta}}{-\cos{2\theta}}
    = \sqmat{a}{b}{b}{-a}
\]
where $R$ is the magnitude and $\theta$ is the direction, and
$R\geq0 \textrm{ and } \theta\in[0,2\pi)$. Since the matrix is symmetric and
traceless, it is only necessary to store two values, $a$ and $b$ to encode
the tensor.

>>>>

\begin{abstract}
This paper addresses the issue of creating modular, extensible code given an
existing solution to a problem, namely, interactively modeling large street
networks. We describe a functional implementation of a framework that allows
users to create a realistic street network over an empty domain, based on the
techniques described in \textit{Interactive Procedural Street Modelling}
\cite{chen}. In particular, we were able to express the underlying mathematics
more intuitively and clearly than is possible in an imperative language.
\end{abstract}

\section{Introduction}
Visual artists often face the time-consuming task of generating extensive,
realistic scenes by hand for movies and video games. However, the apparent
randomness found in systems like street layouts can be modelled effectively
with a variety of mathematical algorithms, giving rise to the growing field of
procedural generation. In this paper we will discuss an algorithm using tensor
fields, from \cite{chen}, to generate realistic city street maps. To facilitate
the generation of aesthetically pleasing maps which fit an artist's
requirements, we implement a simple system of user-specified constraints to
allow the user to shape the resulting street map to fit their needs.

@@

\section{Mathematical Background}
\label{sec:math}
A tensor $t$ is a geometric object represented by a 2x2 symmetric, traceless
matrix:
\[
    \sqmat{\cos{2\theta}}{\sin{2\theta}}{\sin{2\theta}}{-\cos{2\theta}}
    = \sqmat{a}{b}{b}{-a}
\]
where $R$ is the magnitude and $\theta$ is the direction, and
$R\geq0 \textrm{ and } \theta\in[0,2\pi)$. Since the matrix is symmetric and
traceless, it is only necessary to store two values, $a$ and $b$ to encode
the tensor.
